SoK: Transparent Dishonesty: front-running attacks on Blockchain.

### 2019-02-13 frontrunning/Latex/sections/appendix.tex
[Frontrunning] Remove extra stuff from Appendix

\textblue{\textbf{Note to Reviewers:}} If accepted, the camera-ready version will link to a full version of the paper on eprint that will include the information in this appendix. We include it here for reference.

@@

\section{LocalEthereum} \label{app:localethereum}

%Possibly remove this code snippet due to page limit . don't forget to remove the refrence to it ^
\begin{lstlisting}[basicstyle=\scriptsize\ttfamily,caption={Code snippet from LocalEthereum smart contract. Values V,R and S are set by LocalEtherem to have a valid signature, also the tradeHash uses buyer and seller addresses, mitigating the possibility of front-running by a third party.},label={code:localethereum}]
    function createEscrow(bytes16 _tradeID, address _seller, address _buyer, uint256 _value, uint16 _fee,
					uint32 _paymentWindowInSeconds, uint32 _expiry, uint8 _v, bytes32 _r, bytes32 _s) 
        payable external {
        bytes32 _tradeHash = keccak256(abi.encodePacked(_tradeID, _seller, _buyer, _value, _fee));
	...
        // A signature (v, r and s) must come from localethereum to open an escrow
        bytes32 _invitationHash = keccak256(abi.encodePacked(
            _tradeHash,
            _paymentWindowInSeconds,
            _expiry
        )); 
\end{lstlisting}

Code~\ref{code:localethereum} shows a mitigation technique employed by LocalEthereum. \\

>>>>

@@

%\section{LocalEthereum} \label{app:localethereum}
%
%Possibly remove this code snippet due to page limit . don't forget to remove the refrence to it ^
%\begin{lstlisting}[basicstyle=\scriptsize\ttfamily,caption={Code snippet from LocalEthereum smart contract. Values V,R and S are set by LocalEtherem to have a valid signature, also the tradeHash uses buyer and seller addresses, mitigating the possibility of front-running by a third party.},label={code:localethereum}]
%    function createEscrow(bytes16 _tradeID, address _seller, address _buyer, uint256 _value, uint16 _fee,
%					uint32 _paymentWindowInSeconds, uint32 _expiry, uint8 _v, bytes32 _r, bytes32 _s) 
%        payable external {
%        bytes32 _tradeHash = keccak256(abi.encodePacked(_tradeID, _seller, _buyer, _value, _fee));
%	...
%        // A signature (v, r and s) must come from localethereum to open an escrow
%        bytes32 _invitationHash = keccak256(abi.encodePacked(
%            _tradeHash,
%            _paymentWindowInSeconds,
%            _expiry
%        )); 
%\end{lstlisting}
%
%Code~\ref{code:localethereum} shows a mitigation technique employed by LocalEthereum. \\
